---
title: "TRISK Climate Transition Risk Report"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M %Z')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    self_contained: true
params:
  results: NULL
  config: NULL
  run_id: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
```

## Executive Summary

**Run ID:** `r params$run_id`
**Generated:** `r format(Sys.time(), '%Y-%m-%d %H:%M %Z')`

```{r summary_metrics}
df <- params$results
n_companies <- if ("company_id" %in% names(df)) length(unique(df$company_id)) else nrow(df)
total_exposure <- if ("exposure_value_usd" %in% names(df)) sum(df$exposure_value_usd, na.rm = TRUE) else NA

avg_npv <- if ("crispy_perc_value_change" %in% names(df)) {
  mean(df$crispy_perc_value_change, na.rm = TRUE) * 100
} else NA

max_pd <- if ("pd_shock" %in% names(df)) {
  max(df$pd_shock, na.rm = TRUE) * 100
} else NA

format_num <- function(x) {
  if (is.na(x)) return("N/A")
  if (abs(x) >= 1e9) return(paste0(format(round(x / 1e9, 2), scientific = FALSE), "B"))
  if (abs(x) >= 1e6) return(paste0(format(round(x / 1e6, 2), scientific = FALSE), "M"))
  if (abs(x) >= 1e3) return(paste0(format(round(x / 1e3, 2), scientific = FALSE), "K"))
  format(round(x, 2), scientific = FALSE)
}
```

| Metric | Value |
|--------|-------|
| Companies Analyzed | `r n_companies` |
| Total Exposure (USD) | `r format_num(total_exposure)` |
| Average NPV Change | `r if (!is.na(avg_npv)) paste0(round(avg_npv, 2), "%") else "N/A"` |
| Maximum PD Shock | `r if (!is.na(max_pd)) paste0(round(max_pd, 2), "%") else "N/A"` |

---

## Sector Analysis

### NPV Change by Sector

```{r sector_npv, fig.width=8, fig.height=5}
if (all(c("sector", "crispy_perc_value_change") %in% names(df))) {
  sector_data <- df %>%
    group_by(sector) %>%
    summarise(avg_npv_change = mean(crispy_perc_value_change, na.rm = TRUE) * 100,
              .groups = "drop") %>%
    arrange(avg_npv_change)

  ggplot(sector_data, aes(x = reorder(sector, avg_npv_change), y = avg_npv_change,
                          fill = avg_npv_change < 0)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_manual(values = c("TRUE" = "#F53D3F", "FALSE" = "#5D9324"), guide = "none") +
    labs(title = "NPV Change by Sector", x = "", y = "Average NPV Change (%)") +
    theme_minimal(base_size = 12) +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          panel.grid.minor = element_blank())
} else {
  cat("Sector NPV data not available.")
}
```

### PD by Sector: Baseline vs Shock

```{r sector_pd, fig.width=8, fig.height=5}
if (all(c("sector", "pd_baseline", "pd_shock") %in% names(df))) {
  sector_pd <- df %>%
    group_by(sector) %>%
    summarise(avg_pd_baseline = mean(pd_baseline, na.rm = TRUE) * 100,
              avg_pd_shock = mean(pd_shock, na.rm = TRUE) * 100,
              .groups = "drop") %>%
    tidyr::pivot_longer(cols = c(avg_pd_baseline, avg_pd_shock),
                        names_to = "scenario", values_to = "pd") %>%
    mutate(scenario = ifelse(scenario == "avg_pd_baseline", "Baseline", "Shock"))

  ggplot(sector_pd, aes(x = sector, y = pd, fill = scenario)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(values = c("Baseline" = "#5D9324", "Shock" = "#F53D3F")) +
    labs(title = "PD by Sector: Baseline vs Shock", x = "", y = "Avg PD (%)") +
    theme_minimal(base_size = 12) +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.minor = element_blank())
} else {
  cat("Sector PD data not available.")
}
```

---

## PD Results

```{r pd_table}
pd_cols <- c("company_id", "company_name", "sector", "technology",
             "exposure_value_usd", "pd_baseline", "pd_shock")
pd_cols <- intersect(pd_cols, names(df))
if (length(pd_cols) > 0) {
  display <- df[, pd_cols, drop = FALSE]
  if ("pd_baseline" %in% names(display)) display$pd_baseline <- round(display$pd_baseline, 4)
  if ("pd_shock" %in% names(display)) display$pd_shock <- round(display$pd_shock, 4)
  if (all(c("pd_baseline", "pd_shock") %in% names(display))) {
    display$PD_Change <- round(display$pd_shock - display$pd_baseline, 4)
  }
  knitr::kable(head(display, 50), caption = "Top 50 companies by portfolio order")
} else {
  cat("PD data not available.")
}
```

---

## Configuration

```{r config_table}
cfg <- params$config
if (!is.null(cfg)) {
  config_df <- data.frame(
    Parameter = names(cfg),
    Value = sapply(cfg, function(v) paste(v, collapse = ", ")),
    stringsAsFactors = FALSE
  )
  knitr::kable(config_df, caption = "Analysis configuration parameters")
} else {
  cat("Configuration data not available.")
}
```

---

## Disclaimer

This report was generated by the TRISK Climate Transition Risk Stress Testing tool.
The results are based on the scenarios and assumptions configured at the time of analysis.
They should be interpreted in conjunction with professional judgment and are not a substitute
for regulatory capital calculations. All model outputs are subject to the limitations
described in the TRISK methodology documentation.

*Report generated by TRISK Desktop*
